Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-29 manuscript/ERL_global_C_review.Rmd
worked on discussion, tried to knit in new results
@ValentineHerr , the Rmd script is now breaking on line 115. Can you help?

n_fluxes_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_fluxes7])  
n_stocks_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_stocks7])  
n_fluxes_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_fluxes3])  
n_stocks_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_stocks3])  
```

@@

Our analysis reveals a general acceleration of carbon cycling from the tropics to the high latitudes.
For mature forests, this is consistent with a large body of previous work demonstrating that C fluxes generally decline with latitude (or increase with temperature) on a global scale [e.g., @luyssaert_co_2007;  @gillman_latitude_2015; @li_mapping_2019; @banbury_morgan_global_nodate].
The consistency with which this occurs across numerous fluxes is not surprising, but has never been simultaneously assessed across such a large number of variables [but see @banbury_morgan_global_nodate for nine autotrophic fluxes].
Thus, our analysis reveals that carbon cycling is most rapid in the tropics and slowest in boreal regions, including C fluxes into ($GPP$), within (e.g., $NPP$ and its components), and out of (e.g., $R_{soil}$, $R_{eco}$) the ecosystem.

@@

In contrast to the patterns observed for $NEP$ in mature stands, $NEP$ of young forests ...
(discuss NEP well- intuition for some would be that NEP is higher in tropics. Note biome differences for young mut not mature forests, link to latitudinal differences in C sequestration potential [@anderson_temperature-dependence_2006; @cook-patton_mapping_2020]
Lack of synthesis comparing deadwood and organic layer across biomes, but see @cook-patton_mapping_2020 for age trends.

More rapid accumulation of biomass at lower latitudes has been well-established [@anderson_temperature-dependence_2006; @cook-patton_mapping_2020].

For regrowth forests, far less is known about cross-biome differences in carbon cycling. 
However, for most C flux variables, this analysis is the first to examine flux trends in regrowth forests across biomes  (i.e., age x biome interaction).
Data remain sparse, but for better-represented variables, we often see faster acceleration of C cycling in the warmer climates.
Further work will be required to explore age x climate interactions, but our broad-brush overview indicates that C cycling of regrowth forests is not only higher in the tropics, parallel to fluxes in mature forests [ @banbury_morgan_global_nodate], but also that it accelerates more rapidly with stand age in the tropics, consistent with more rapid biomass accumulation.

>>>>

n_fluxes_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_fluxes7])  
n_stocks_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_stocks7]) #BREAKS HERE
n_fluxes_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_fluxes3])  
n_stocks_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_stocks3])  
```

@@

Our analysis reveals a general deceleration of carbon cycling from the tropics to boreal regions.
For mature forests, this is consistent with a large body of previous work demonstrating that C fluxes generally decline with latitude (or increase with temperature) on a global scale [e.g., @luyssaert_co_2007;  @gillman_latitude_2015; @li_mapping_2019; @banbury_morgan_global_nodate].
The consistency with which this occurs across numerous fluxes is not surprising, but has never been simultaneously assessed across such a large number of variables [but see @banbury_morgan_global_nodate for nine autotrophic fluxes].
Thus, our analysis reveals that carbon cycling is most rapid in the tropics and slowest in boreal regions, including C fluxes into ($GPP$), within (e.g., $NPP$ and its components), and out of (e.g., $R_{soil}$, $R_{eco}$) the ecosystem.

@@

In contrast to the patterns observed for $NEP$ in mature stands, $NEP$ of stands between 20 and 100 years of age varied across biomes, being lowest in boreal forests, intermediate in temperate broadleaf forests, and highest in temperate conifer forests (with insufficient data to assess tropical forests; Figs. 6f, S1).
This is consistent with findings that live biomass accumulation rates (*e.g.*, $\Delta B_{ag}$ or $\Delta B_{tot}$) during early secondary succession decrease with latitude [@anderson_temperature-dependence_2006; @cook-patton_mapping_2020; Figs. 7a, S16-S22]. 
Note, though, that $NEP$ includes not only $\Delta B_{tot}$, but also changes in $DW_{tot}$, $OL$, and soil carbon, and biome differences in the accumulation rates of these variables have not been detected, in part because these variables do not consistently increase with stand age [@cook-patton_mapping_2020; Figs. 7, S23-S26; see discussion below].

For regrowth forests, little is known about cross-biome differences in carbon fluxes, and we are not aware of any previous large-scale comparisons of C fluxes that have been limited to regrowth forests [although they're commonly mixed in with mature forests; e.g., **REFS**]. 
Thus, this analysis was the first to examine flux trends in regrowth forests across biomes.
The observed tendency for young forest fluxes to decrease from tropical to boreal regions paralleled patterns in mature forests (Figs. 6, S1-S15), suggesting that regrowth forests follow latitudinal trends in carbon cycling similar to those of mature forests [e.g., @banbury_morgan_global_nodate].
*Yet, data remain sparse, and further work will be required to explore age x climate interactions.Nevertheless, our broad-brush overview indicates that C cycling of regrowth forests is not only higher in the tropics, parallel to fluxes in mature forests [@banbury_morgan_global_nodate], but also that it accelerates more rapidly with stand age in the tropics, consistent with more rapid biomass accumulation.*
